---
 author here - Kiet Bastiaans
  name reviewer here - Viktor
date: "`r format(Sys.time(15-2-2022), '%12 %2, %2022')`"
---


##title: "Assigment - kNN DIY"
#author:
 - # author here - Kiet Bastiaans
- #name reviewer here - Viktor
date: "`r format(Sys.time(25-2-2022), '%12 %2, %2022')`"
output:
   html_notebook:
    toc: true
    toc_depth: 2


#prep
```{r}
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
```

## Business Understanding
#the Goal of collection of this data: To lower energy consumption by appropriate controlof HVAC and lighting systems in buildings. Other applications for occupancy detection include security and determination of building occupant behaviors. A system that could accurately detect the presence of the occupants without using a camera is very interesting due to privacy concerns.

#Accurate occupancy detection of an office room from light,temperature, humidity and CO2 measurements.

#source: Luis Candanedo, luismiguel.candanedoibarra '@' umons.ac.be, UMONS.





## Data Understanding
```{r} 
##upload KNN_occupancy data set from from github
KNN<-KNN_occupancy 
#Easier Name to write :)  

#Viktor's comment: It is better to use the path since if i don't have the data downloaded i cannot work on the model so my improved version would be the following 

url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/data-mining-s2y2122-vicsubzero/master/datasets/KNN-occupancy.csv"
    
KNN <- read_csv(url)
```

```{r}
str(KNN) 
#This data set has 7 Variables(columns) and 8143 Observations(rows) 
```

## Data Preparation
```{r}
KNNC <- KNN[-1] #the first colum (date had no relevance)
head(KNNC)
```
```{r}
cntDiag<- table(KNNC$Occupancy) #we would like to predict if the room was occupied or not so I the diagnosis to predict the column Occupancy

propDiag <- round(prop.table(cntDiag) * 100 , digits = 1)                

cntDiag   # 0 means unoccupied 1 means occupied
```


```{r}
propDiag
```
```{r}
KNNC$Occupied <- factor(KNNC$Occupancy, levels = c("0", "1"), labels = c("Occupied", "unoccupied")) %>% relevel("Occupied")
head(KNNC, 50)
```
```{r}
summary(KNNC[c("Light","Temperature","Humidity", "CO2")])
```

```{r}
normalize <- function(x) { # Function takes in a vector
  return ((x - min(x)) / (max(x) - min(x))) # distance of item value - minimum vector value divided by the range of all vector values
}

testSet1 <- c(0:5)
testSet2 <- c(0:5) * 10

cat("testSet1:", testSet1, "\n")
```
```{r}
cat("testSet2:", testSet2, "\n")
```
```{r}
cat("Normalized testSet1:", normalize(testSet1), "\n")
```
```{r}
cat("Normalized testSet2:", normalize(testSet2))
```
```{r}
nCols <- dim(KNNC)[2] # with this code it makes all variables equally important so that bigger differences don't have a bigger impact :) 
KNNC_n <- sapply(1:(nCols-1),
function(x) {
 
normalize(KNNC[,x])
}) %>% as.data.frame()

summary(KNNC_n)
```
```{r}
#KNNtrain_feat <- KNNC_n[1:1200,]
#KNNtest_feat <- KNNC_n[1200:8143,]

#Viktor: The numbers overlap that is the problem 

#Solution 

KNNtrain_feat <- KNNC_n[1:1199, ]
KNNtest_feat <- KNNC_n[1200:8143, ]
```


```{r}
#KNNtrain_labels <- KNNC[1:1199, 1]  
#KNNtest_labels <- KNNC[1200:8143, 2]

# Viktor : the columm that the labels were looking are wrong it should be columm number 7 becouse that is the one containing the occupaid or not 

KNNtrain_labels <- KNNC[1:1199, 7]  
KNNtest_labels <- KNNC[1200:8143, 7]
```

## Modeling
```{r}
KNNC_test_pred <- knn(train = as.matrix(KNNtrain_feat), test = as.matrix(KNNtest_feat), cl = as.matrix(KNNtrain_labels), k = 21)

head(KNNC_test_pred)
```
## Evaluation and Deployment
```{r}
confusionMatrix(KNNC_test_pred, KNNtest_labels[[1]], positive = NULL, dnn = c("Prediction", "True"))


```

#reviewer adds suggestions for improving the model

